\LARGE \bf Planning with Attitude

### 2020-10-14 paper/main.tex

    \begin{equation}
    	\phi_k = ({\nabla r}^T {\nabla r})^{-1} {\nabla r}^T r(q_k).
    \end{equation}
	The update is then applied using the composition for the group:
	\begin{equation}
		\q_{k+1} = \q_k \otimes \varphi(\phi_k)
	\end{equation}.
	This ``multiplicative'' Gauss-Newton method is summarized in Algorithm \ref{alg:mgn}.

@@

        \begin{figure}[ht]
            \centering
            \includegraphics[width=\columnwidth]{figures/barrellroll.png}
            \caption{Barrel roll trajectory computed by ALTRO using a terminal cost to encourage an upside-down attitude.}
            \label{fig:barrellroll}
        \end{figure}

        \begin{figure}[ht]
            \centering
            \includegraphics[height=4cm,width=\columnwidth]{figures/c_max_convergence.tikz}
            \caption{Constraint satisfaction as a function of iteration when solving the barrel roll problem using ALTRO both with and without the modifications for optimizing unit quaternions.}
            \label{fig:c_max_convergence}
        \end{figure}

    \subsection{Quadrotor Flip}
        A 360 degree flip trajectory for a quadrotor was optimized with dynamics adapted
        from \cite{mellinger2012trajectory}. To encourage the flip, we specified a 
        ``waypoint'' cost function of the following form:
        \begin{multline}
                  \sum_{k \in \mathcal{N}} \ell(x_k, \hat{x}, \hat{Q}) 
                + \sum_{k \in \mathcal{W}} \ell(x_k, \bar{x}_k, Q_w) 
                + \half \sum_{k=1} u_k^T R u_k
        \end{multline}
        with $\mathcal{W} = \{45,51,55,75,101\}$, $\mathcal{N} = \{1:101\} \setminus
        \mathcal{W}$. The four intermediary ``waypoints'' were used to encourage the
        quadrotor to reach angles of \ang{90}, \ang{180}, \ang{270}, and \ang{360} around
        an approximately circular arc. The last waypoint was used to encourage the
        quadrotor to move towards the final goal. The quadrotor was constrained to stay
        above the floor and move to a goal state two meters away in the $+y$ direction. The
        solver was provided a dynamically infeasible initial trajectory that linearly
        interpolates between the initial and final states, rotating the quadrotor around
        the x-axis a full \ang{360}.

@@

\section*{Acknowledgements}
This work was supported by a NASA Early Career Faculty Award (Grant Number 80NSSC18K1503). This material is based upon work supported by the National Science Foundation Graduate
Research Fellowship Program under Grant No. DGE-1656518. Any opinions, findings, and
conclusions or recommendations expressed in this material are those of the author(s) and
do not necessarily reflect the views of the National Science Foundation.

>>>>

    \begin{equation}
    	\phi_k = ({\nabla r}^T {\nabla r})^{-1} {\nabla r}^T r(q_k).
    \end{equation}
	The update is then applied using the composition for the group:
	\begin{equation}
		\q_{k+1} = \q_k \otimes \varphi(\phi_k).
	\end{equation}
	This ``multiplicative'' Gauss-Newton method is summarized in Algorithm \ref{alg:mgn}.

@@

        \begin{figure}[t]
            \centering
            \includegraphics[width=\columnwidth]{figures/barrellroll.png}
            \caption{Barrel roll trajectory computed by ALTRO using a terminal cost to encourage an upside-down attitude.}
            \label{fig:barrellroll}
        \end{figure}

        \begin{figure}[t]
            \centering
            \includegraphics[height=4cm,width=\columnwidth]{figures/c_max_convergence.tikz}
            \caption{Constraint satisfaction as a function of iteration when solving the barrel roll problem using ALTRO both with and without the modifications for optimizing unit quaternions.}
            \label{fig:c_max_convergence}
        \end{figure}

    \subsection{Quadrotor Flip}
        A 360 degree flip trajectory for a quadrotor was optimized with dynamics adapted
        from \cite{mellinger2012trajectory}. To encourage the flip, we specified a 
        ``waypoint'' cost function of the following form:
        \begin{multline}
                  \sum_{k \in \mathcal{N}} \ell(x_k, u_k, \hat{x}, \hat{Q}, R) 
                + \sum_{k \in \mathcal{W}} \ell(x_k, u_k, \bar{x}_k, Q_w, R) 
        \end{multline}
        where $\hat{x}$, $\hat{Q}$ are the nominal state and state weight matrix, $Q_w$ is 
        the weight matrix for the waypoints, and
        $\mathcal{W} = \{45,51,55,75,101\}$, $\mathcal{N} = \{1:101\} \setminus
        \mathcal{W}$.
        Four intermediary ``waypoints'' were used to encourage the
        quadrotor to reach angles of \ang{90}, \ang{180}, \ang{270}, and \ang{360} around
        an approximately circular arc. The last waypoint was used to encourage the
        quadrotor to move towards the final goal. The quadrotor was constrained to stay
        above the floor and move to a goal state two meters away in the $+y$ direction. The
        solver was provided a dynamically infeasible initial trajectory that linearly
        interpolates between the initial and final states, rotating the quadrotor around
        the x-axis a full \ang{360}.

@@

\section*{Acknowledgements}
This work was supported by a NASA Early Career Faculty Award (Grant Number 80NSSC18K1503).
This research was carried out in part at the Jet Propulsion Laboratory, California Institute of Technology, under a contract with the National Aeronautics and Space Administration and funded through JPL’s Strategic University Research Partnerships (SURP) program.
This material is based upon work supported by the National Science Foundation Graduate
Research Fellowship Program under Grant No. DGE-1656518. Any opinions, findings, and
conclusions or recommendations expressed in this material are those of the author(s) and
do not necessarily reflect the views of the National Science Foundation.
